HydroFlow: A New Dataflow Programming Language

### 2022-11-02 notes/types.tex
new directory
the axiom transformations continue to prove somewhat confusing.

    {
      \inferrule[pivot]{|\outputs(\op)| = |p'| \\ 
        C ⊢ p : d \\ C';d ▷ op[0] ⊢ p'}
                {{C,C'} ⊢ [p]\op[p']}}

    {
      \inferrule[inward]{C ⊢ p : d}
                {{C} ⊢ [p]\op : d ▷ \op[0]}}

{
      \inferrule[outward]{\outarity(\op) = |p'| \\
        C;d ▷ \op[0] ⊢ p'}
                {{C};d ⊢ \op[p']}}

@@

{\inferrule[axiom-transform-option1]{\forall s. d(s) \subseteq d'(s)}{Γ ⊢ d ⇝ d'}}

{\inferrule[axiom-transform-option2]{d \subseteq d'}{Γ ⊢ d ⇝ d'}}

{\inferrule[axiom-transform-option3]{pre(d) \rightarrow pre(d') 
 \\ post(d') \rightarrow post(d)}{Γ ⊢ d ⇝ d'}}

{\inferrule[axoim-transform-abstract]{Γ,dₐ▷A : τₐ ⊢ d ⇝ d' \\ A~\fresh}{Γ ⊢ d[A/dₐ] ⇝ d'}}

{\inferrule[axoim-transform-concretize]{τₐ <: τ}{Γ,dₐ▷A : τₐ ⊢ d ⇝ d["?s"~τ/dₐ]}}

{\inferrule[axoim-transform-transitive]{Γ ⊢ d ⇝ d' \\ Γ ⊢ d' ⇝ d''}{
Γ ⊢ d ⇝ d''}}

{\inferrule[axoim-transform-unfold]{}{Γ,dₐ▷A : τₐ  ⊢ d ⇝ d[A/dₐ]}}

{\inferrule[axoim-transform-fold]{}{Γ,dₐ▷A : τₐ  ⊢ d[A/dₐ] ⇝ d}}

{\inferrule[axoim-transform-reflexive]{}{Γ ⊢ d ⇝ d}}

@@

Worth wondering if we're going to be in trouble overloading the $[]$ syntax here; time will tell. 
Types appear in figure \ref{fig:types}. 
Another concern is that we have a uhhh _lot_ of type systems in the mix at this point: 
we've got $C;d ⊢ p$, $C ⊢ p : d$, $Γ ⊢ d : τ$, and $Γ ⊢ d ⇝ d'$.  
That's a lot more independent systems than we'd ideally  have.  Is there a way to collapse this back down?

>>>>

    {
      \inferrule[pivot]{|\outputs(\op)| = |p'| \\ 
        C ⊢ p : d \\ C';d ▷ op[0] ⊢ p'}
                {{C,C'} ⊢ (p)\op(p')}}

    {
      \inferrule[inward]{C ⊢ p : d}
                {{C} ⊢ (p)\op : d ▷ \op[0]}}

{
      \inferrule[outward]{\outarity(\op) = |p'| \\
        C;d ▷ \op[0] ⊢ p'}
                {{C};d ⊢ \op(p')}}

@@

%{\inferrule[axiom-transform-option1]{\forall s. d(s) \subseteq d'(s)}{Γ ⊢ d ⇝ d'}}

{\inferrule[axiom-transform]{d \subseteq d'}{ ⊢ d ⇝ d'}}

%{\inferrule[axiom-transform-option3]{pre(d) \rightarrow pre(d') 
% \\ post(d') \rightarrow post(d)}{Γ ⊢ d ⇝ d'}}

     {\inferrule[axiom-transform-abstract]{Γ,dₐ▷A : τₐ ⊢ d ⇝ d' \\ A~\fresh}{Γ ⊢ d[A/dₐ] ⇝ d'}}

{\inferrule[axiom-transform-concretize]{τₐ <: τ \\ Γ ⊢ dₐ : τₐ}{Γ ⊢ d ⇝ d["?s"~τ/dₐ]}}

{\inferrule[axiom-transform-unfold]{}{Γ,dₐ▷A : τₐ  ⊢ d ⇝ d[A/dₐ]}}\MPM{ideally we'd find a way to do this one item at a time, not all-at-once like this. Also, to both sides of the ⇝.}

{\inferrule[axiom-transform-fold]{}{Γ,dₐ▷A : τₐ  ⊢ d[A/dₐ] ⇝ d}}\MPM{Same comment here.}

@@

Types appear in figure \ref{fig:types}. 
Another concern is that we have a uhhh _lot_ of type systems in the mix at this point: 
we've got $C;d ⊢ p$, $C ⊢ p : d$, $Γ ⊢ d : τ$, and $Γ ⊢ d ⇝ d'$.  
That's a lot more independent systems than we'd ideally  have.  Is there a way to collapse this back down?
